---
title: "Dealing with NA/NULL/NaN"
output: 
    html_document:
        toc: true
        toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# In general

In R there are several type of special values such as `NA`, `NaN` and `NULL`. They are similar but at the same time different especially when directly tested. In general:

- `NA` is a missing information
- `NaN` means *not a number* and is the result of an not-defined math operation like $\frac{0}{0}$.
- `NULL` is the absence of any information

# Type

In terms of data type, `NA` is *logical*, `NaN` is *numeric* type and `NULL` do not have a specific type. A particularity of `NA` is that can be also adapted to the type of vector where is located. In R we cannot have a vector of `numbers` and `logical` values:

```{r}
is.logical(NA)
is.logical(NaN)
is.logical(NULL)

vec <- c(1,2,3,4, TRUE, 5, FALSE)
vec # TRUE is 1 and FALSE is 0
```

But we can have a *numeric*, *character* or *logical* vector with `NA` values and the `NA` is forced to the specific type:

```{r}
# NA alone is logical but

vec <- c(1,2,3,4,NA,5,6)
class(vec)

for(i in vec) print(class(i))

# now NA is numeric
```

This is possible because there are several type of `NA` values that are not usually employed directly but are used from R depending on the vector:

```{r}
is.character(NA_character_)
is.numeric(NA_real_)
is.integer(NA_integer_)

# This

vec <- c(1,2,3,4,5,NA)
vec

# is the same as

vec <- c(1,2,3,4,5,NA_integer_)
vec
```

The `NaN` is a numeric type because is the result of *undefined operations*:

```{r}
is.numeric(NaN)

0/0

vec <- c(1,2,3,4,NaN)
vec
```

The `NULL` value is surely the strangest because represents the absence of any value and the class is `NULL` itself meaning that is different from `NA` and `NaN` values.

```{r}
x <- NULL
class(x) # the class is NULL
```
Compared to `NA` and `NaN` that are associate with some information (absence of value and undefined number), `NULL` values are somehow transparent and cannot be stored in vectors:

```{r}
vec <- c(1,2,3,4,5, NA, 8, NaN, 11, NULL)
vec # the null value is not present
```

# The problem with `NA`

As Hadley suggest[^na_hadley] the `NA` values infect all other computations. Practically many R functions such as `mean()` or `sd()` cannot return a value if there is a `NA` within the target vector.

```{r}
x <- c(runif(10), NA)
mean(x)
sd(x)
```

In fact, these functions have a specific argument `na.rm = TRUE` for doing the computation without considering `NA` values. Of course we can remove `NA` values before the computation and the result will be the same:

```{r}
mean(x, na.rm = TRUE)
mean(x[!is.na(x)])
```

[^na_hadley]: 

# Sources

- http://www.cookbook-r.com/Basics/Working_with_NULL_NA_and_NaN/
- https://www.projectpro.io/recipes/what-is-difference-between-na-and-nan-r