---
title: ""
subtitle: ""
author: ""
institute: ""
date: ""
output:
  xaringan::moon_reader:
    seal: false
    css: ["resources/arca.css", "resources/arca_fonts.css"]
    lib_dir: libs
    nature:
      highlightStyle: googlecode
      highlightLines: true
      highlightLanguage: ["r"]
      countIncrementalSlides: false
      ratio: "16:9"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```
class: title-slide, center, middle

#.title[Introduzione a R]

#.subtitle[Giornata 1]

```{r, out.width="10%", echo = FALSE}
knitr::include_graphics(path = "img/tidyverse.svg")
```


###.location[Corsi ARCA - @DPSS]

###.author[Filippo Gambarota]

---

# Header 1

## Header 2

### Header 3

#### Header 4

---

# Test font

- bullet 1
- bullet 2
- bullet 3

---

# Test font

This is a **font** test. It's awesome! you can use all *fonts* that you want. This is an `inline code`

---

# Colors

Colored fonts test!

* This is a .red[red color]
* This is a .blue[blue color]
* This is a .green[green color]
* This is a .yellow[yellow color]

---
class: section, middle, center

# Section 1

---

# Code

```{r, eval=FALSE}
data[rows, columns]
data[rows, columns]
data[rows, columns]
{{data[rows, columns]}}
data[rows, columns]
```